### 2025-08-12 data-visualization.qmd
20250811 - function prefixes

- [histogram](#sec-histogram): `geom_histogram()`
- [density plot](#sec-densityPlot): `geom_density()`
- [box-and-whisker plot](#sec-boxAndWhiskerPlot): `geom_boxplot()`
- [violin plot](#sec-violinPlot): `geom_violin()`
- [bar plot](#sec-barPlot): `geom_bar()`
- [scatterplot](#sec-scatterplot): `geom_point()`
- [rug plot](#sec-scatterplotRugPlot): `geom_rug()`
- [line chart](#sec-lineChart): `geom_line()`
- statistical summary (e.g., [best-fit line](#sec-scatterplotBestFitLine)): `geom_smooth()`

>>>>

- [histogram](#sec-histogram): `ggplot2::geom_histogram()`
- [density plot](#sec-densityPlot): `ggplot2::geom_density()`
- [box-and-whisker plot](#sec-boxAndWhiskerPlot): `ggplot2::geom_boxplot()`
- [violin plot](#sec-violinPlot): `ggplot2::geom_violin()`
- [bar plot](#sec-barPlot): `ggplot2::geom_bar()`
- [scatterplot](#sec-scatterplot): `ggplot2::geom_point()`
- [rug plot](#sec-scatterplotRugPlot): `ggplot2::geom_rug()`
- [line chart](#sec-lineChart): `ggplot2::geom_line()`
- statistical summary (e.g., [best-fit line](#sec-scatterplotBestFitLine)): `ggplot2::geom_smooth()`
